Online {\IterComp}

### 2017-09-15 motivation.tex
motivation and setup

    Prior to this paper there were two proposed metrics to correlate with program efficiency. The first is simply to use runtime, ignoring
    the work aspect. This functions well when the inputs all require similar effort. When that is not the case it bears little or no
    correlation to efficiency. The second approach is \textit{instructions per cycle}~(IPC), suggested by~\citep{fursin07}. While IPC seems
    promising in the sense that faster instruction execution is a good thing, this is belied by the simple observation that adding
    redundant NOPs to a program will increase IPC while also slowing the program down. Figure~\ref{fig:motivation-metric} shows the
    relationship between execution time, IPC and speedup for different optimizations of \texttt{susan\_c}, averaged across a subset of the
    inputs. Neither IPC nor execution time correlate well, and so neither can be used for iterative compilation. We need a work efficiency
    metric which can approximate speedup instead, using only a single execution.

>>>>

    Prior to this paper there were two proposed metrics to correlate with program efficiency. The first is simply to use runtime, ignoring
    the work aspect. This functions well when the inputs all require similar effort. When that is not the case it bears little or no
    correlation to efficiency. The second approach is \textit{instructions per cycle}~(IPC), suggested by~\citep{fursin07}. While IPC seems
    promising in the sense that faster instruction execution is a good thing, this is belied by the simple observation that adding
    redundant NOPs to a program will increase IPC while also slowing the program down. Figure~\ref{fig:motivation-metric} shows the
    relationship between execution time, IPC and speedup for different optimizations of \texttt{susan\_c}, averaged across a subset of the
    inputs. We use correlation coefficient~\cite{Bishop:2006:PRM:1162264} to quantify if  IPC and execution time is strongly correlated to
    speedup. This correlation coefficient takes a value between -1 and 1, the closer the coefficient is to +/-1, the stronger the
    correlation between the variables. In our case, the IPC and execution time show correlation coefficients of $-0.14$ and $-0.16$,
    respectively, to speedup. These values are far from 1, suggesting that there is a weak correlation between speedup and IPC or
    execution time. Clearly, neither IPC nor execution time correlate well, and so neither can be used for iterative compilation. We need a work efficiency
    metric which can approximate speedup instead, using only a single execution.
